\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-03-13 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
explained what is done if PML elements are viscoelastic or poroelastic

The next release of the code will include support Convolution or Auxiliary Differential Equation Perfectly Matched absorbing Layers
(C-PML or ADE-PML) \citep{KoMa07,MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10}.
It will also use the PT-SCOTCH parallel and threaded version of SCOTCH for mesh partitioning instead of the serial version.\\

@@

>>>>

The next release of the code will include support Convolution or Auxiliary Differential Equation Perfectly Matched absorbing Layers
(C-PML or ADE-PML) \citep{MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10,KoMa07}.
It will also use the PT-SCOTCH parallel and threaded version of SCOTCH for mesh partitioning instead of the serial version.\\

@@

If you use PML, the mesh elements that belong to the PML layers can be acoustic or elastic, but not viscoelastic nor poroelastic.
Then, when defining your model, you should define these absorbing elements as either acoustic or elastic.
In you forget to do that, the code will fix the problem by automatically converting the viscoelastic or poroelastic PML
elements to elastic. This means that strictly speaking the PML layer will not be perfectly matched any more, since the physical
model will change from viscoelastic or poroelastic to elastic at the entrance of the PML, but in practice this is sufficient and
produces only tiny / negligible spurious reflections.
